Parsing Tweets into Universal Dependencies

### 2018-04-15 paper.tex
copyedits to paper and bib; clarification

\subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
The first Twitter treebank annotated with Universal Dependencies 
was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
which consists of 6,738 tweets (119,726 tokens).
In their convention, tokenization tends to preserve the original
tweet content but two special cases, \textit{articulated prepositions}
(e.g. \textit{nella} as \textit{in la})
and \textit{clitic clusters} (e.g. \textit{guardandosi} as \textit{guardando si}), are tokenized.
\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
%Beyond tokenization, an extra layer of lemmas is annotated
%to recover ``what is understandable by a human''.
%It's arguable whether normalization (the lemmatization in \citet{sanguinetti-17})
%on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
%In this paper, we don't include normalization and leave it an open question for further study.
%\nss{Maybe just say: 
Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
The current UD guidelines on lemmas give a lot of flexibility on treebank development.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
%You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
%developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretation of headedness is the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while \citet{sanguinetti-17} used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
The choice of relation on the non-syntactic tokens is questionable
since UD doesn't specify a convention for this. 
Our choice of \textit{discourse} is inspired by the observation that emoticon is annotated as \textit{discourse}.
\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.\nss{what did PosTWITA-UD use for non-syntactic tokens?}\yjcomment{done}
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer\footnote{We choose Stanford CoreNLP tokenizer in the spirit of comparing rule-based and statistical model-based method.}, %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.

@@

\section*{Acknowledge}
We thank Elizabeth Clark, Lucy Lin, Nelson Liu, Kelvin Luu, Phoebe Mulcaire, 
Hao Peng, Maarten Sap, Chenhao Tan, and Sam Thomson at the University of Washington, 
and Austin Blodgett, Lucia Donatelli, Joe Garman, Emma Manning, Angela Yang, and Yushi Zhang 
at Georgetown University for their annotation efforts in the first round.
We are grateful for the support from Lingpeng Kong at the initial stage of this project.
We also thank the anonymous reviewers for their helpful comments and suggestions.
\yjcomment{funding agency here and anyone else i miss.}
This work was supported by the National Key Basic Research
Program of China via grant 2014CB340503 and the
National Natural Science Foundation of China (NSFC) via
grant 61632011.

>>>>

\subsection{Comparison to PoSTWITA-UD}\label{sec:postwita}
The first Twitter treebank annotated with Universal Dependencies 
was the \mbox{\textit{PosTWITA-UD}} corpus for Italian \citep{sanguinetti-17}, 
which consists of 6,738 tweets (119,726 tokens).
In their convention, tokenization tends to preserve the original
tweet content but two special cases, \textit{articulated prepositions}
(e.g.~\textit{nella} as \textit{in la})
and \textit{clitic clusters} (e.g.~\textit{guardandosi} as \textit{guardando si}), are tokenized.
%\nss{explain what these two phenomena are. are these the only words that are split?}\yjcomment{done}
%Beyond tokenization, an extra layer of lemmas is annotated
%to recover ``what is understandable by a human''.
%It's arguable whether normalization (the lemmatization in \citet{sanguinetti-17})
%on social media data is essential according to \citet{eisenstein:2013:NAACL-HLT}.
%In this paper, we don't include normalization and leave it an open question for further study.
%\nss{Maybe just say: 
Their lemmas include spelling normalization, whereas our lemmas only normalize casing and inflectional morphology.
The current UD guidelines on lemmas give a lot of flexibility on treebank development.\footnote{\url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}
%You could also mention that the current UD guidelines on lemmas (which I wrote) give a lot of flexibility to treebank 
%developers: \url{http://universaldependencies.org/u/overview/morphology.html\#lemmas}}

%In the syntax annotation, tweet specific
%constructions are considered by both \citet{sanguinetti-17} and our paper.
With respect to tweet-specific constructions,
\citeposs{sanguinetti-17} and our  interpretation of headedness is the same, 
but we differ in the relation label.
For topical hashtags, we use \textit{discourse} while \citet{sanguinetti-17} used \textit{parataxis}. 
In referential URLs, we use \textit{list} (following the precedent of UD\_English-EWT) while \citet{sanguinetti-17} used \textit{dep}.
%The choice of relation on the non-syntactic tokens is questionable
%since UD doesn't specify a convention for this. 
Our choice of \textit{discourse}\nss{for what? maybe the previous sentences should be swapped} is inspired by the observation that emoticons are annotated as \textit{discourse}.\nss{by whom?}
\citet{sanguinetti-17} used the same relation for the emoticon but analyze topical hashtag as \textit{parataxis}.
\nss{topical hashtags already mentioned above}
% Non-syntactic tokens can be easily recovered
% from our annotation and changing it to other relation in the future development is not difficult.
We expect that the official UD guidelines will eventually adopt standards for these constructions so the treebanks can be harmonized.

@@

\paragraph{Pipeline evaluation.} Finally, we report  our full
pipeline's performance in  Table \ref{tbl:pipline}. We also compare
our model with a pipeline of the state-of-the-art systems (labeled  ``SOTA''):
Stanford CoreNLP tokenizer,\footnote{We choose the Stanford CoreNLP tokenizer in the spirit of comparing 
rule-based and statistical methods.} %\yicomment{why not compare with UDPipe?}\yjcomment{i was thinking stanford tokenizer is more suitable, but i will get the udpipe result},
\citet{owoputi-EtAl:2013:NAACL-HLT}'s tagger, and \citet{dozat-qi-manning:2017:K17-3}'s parser.
Our system differs from the SOTA pipeline in the tokenization and parser components.
From Table \ref{tbl:pipline}, our pipeline outperforms the SOTA when
evaluated in pipeline manner.
The results also emphasize the
importance of tokenization:  without gold tokenization
%\nascomment{changed ``segmentation'' to ``tokenization'' here, twice},
UD parsing
performance drops by more than four points.

@@

\section*{Acknowledgments}
We thank Elizabeth Clark, Lucy Lin, Nelson Liu, Kelvin Luu, Phoebe Mulcaire, 
Hao Peng, Maarten Sap, Chenhao Tan, and Sam Thomson at the University of Washington, 
and Austin Blodgett, Lucia Donatelli, Joe Garman, Emma Manning, Angela Yang, and Yushi Zhang 
at Georgetown University for their annotation efforts in the first round.
We are grateful for the support from Lingpeng Kong at the initial stage of this project.
We also thank the anonymous reviewers for their helpful comments and suggestions.
\yjcomment{funding agency here and anyone else i miss.}
This work was supported by the National Key Basic Research
Program of China via grant 2014CB340503 and the
National Natural Science Foundation of China (NSFC) via
grant 61632011.

\nss{bibliography: most but not all conference papers have URLs; some but not all have page numbers. 
``TACL'' is sometimes spelled out.
Make sure ``LSTM'', ``LSTMs'', etc. are capitalized properly in titles.}
